A new tidy data structure to support exploration and modeling of temporal data

### 2019-01-19 main.Rmd
done with conclusions

A new data abstraction representing temporal data named as "tsibble" has been proposed, spotlighting the "tidy data" principles brought to time domain. Tidy data begins to take shape in the state of time with the introduction of contextual semantics: index and key. Declared index provides direct support to time variable; variables that comprise the key defines study subjects over time. These semantics further determines unique data entries required for a valid tsibble. No matter how temporal data arrives, tsibble respects time index and keeps data richness. A tsibble frictionlessly pops into transformation, visualization, modelling and smoothly shifts amongst, allowing for rapid iterations in gaining data insights.

A missing piece of the *tsibble* data is to enable user-defined calendars and respect structural missing observations. For example, a call center operates only between 9:00am and 5:00pm on week days and stock trading resumes on Monday straight after Friday. No data available outside trading hours would be labelled as structural missingess, which *tsibble* currently disregards. However, few R packages provide functionality to create and manage many sorts of calendars, including market-specific business calendar. This delays the implementation. Generally, custom calendars would be easily embedded into the tsibble framework. Consequently these tsibble operators, like `fill_gaps()`, would work out of box; forecasts would be generated within its definable time range.

>>>>

A new data abstraction to represent temporal data named as "tsibble" has been presented, spotlighting the "tidy data" principles brought to time domain. Tidy data begins to take shape in the state of time with the introduction of contextual semantics: index and key. A declared index provides direct support to time variable; variables that comprise the key define observations over time. These semantics further determine unique data entries required for a valid tsibble. No matter how temporal data arrives, tsibble respects a time index and mainatins the data richness. A tsibble frictionlessly pops into transformation, visualization, modelling and smoothly shifts between, allowing for rapid iteration to gain data insights.

A missing piece of the *tsibble* data is to enable user-defined calendars and respect structural missing observations. For example, a call center operates only between 9:00am and 5:00pm on week days and stock trading resumes on Monday straight after Friday. No data available outside trading hours would be labelled as structural missingess, which *tsibble* currently disregards. However, few R packages provide functionality to create and manage many sorts of calendars, including market-specific business calendar. <!-- This delays the implementation.--> Generally, custom calendars would be easily embedded into the tsibble framework. Consequently these tsibble operators, like `fill_gaps()`, would work out of box, and forecasts would be generated within its definable time range.
